Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-02-13 manuscript/phylogenetic_signal_manuscript.tex
working on DBS comments

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals~\citep{Schemske1999}.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
  In particular, significant phylogenetic signal in plants' interaction partners
  ---the tendency for more closely-related plants to have more similar interactions---
  tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
  Further, plants' roles within networks tend to be less phylogenetically constrained than those of 
  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}.

@@

  A further complication is the possibility that the relationship between
  plants' relatedness and the similarity of their interaction partners is
  not constant across plant clades. Closely-related plants
  in one clade might be under strong selection to favour dissimilar
  sets of pollinators to avoid exchanging pollen with other
  species~\citep{Levin1970,Bell2005,Mitchell2009}. Similar pressures 
  could also affect related plants' defences against herbivores if 
  congeners tend to grow in the same places such that herbivores 
  could easily move between them.  Unrelated plants might also 
  converge upon similar phenotypes, attracting a particularly 
  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009}. 
  Likewise, herbivores may be able to depredate sets of unrelated 
  plants if they have evolved similar defences~\citep{Pichersky2000}. 
  In either case, dissimilarity of interactions among related species 
  or similarity of interactions among unrelated species could result 
  in low apparent phylogenetic signal across an entire plant community. 
  Moreover, all of the aforementioned hypotheses 
  are non-exclusive; different processes likely affect different
  clades, and these processes might be associated with different 
  pressures imposed by pollination and herbivory.

  Here we use a novel approach to investigate how the patterns of
  overlap in interaction partners between pairs of plants (henceforth
  ``niche overlap'') vary over phylogenetic distance. Whereas previous
  studies have focused on the presence or absence of phylogenetic
  signal across entire networks, we are able to investigate the
  relationship between niche overlap and phylogenetic distance in
  within networks as well as different plant families. Specifically,
  we test whether niche overlap decreases over increasing phylogenetic
  distance in a large dataset of pollination and herbivory networks, 
  whether the plant family composition of a community affects the
  relationship between niche overlap and phylogenetic distance in that community,
  and whether the relationship between niche overlap and phylogenetic
  distance differs across plant families.

@@

  We studied phylogenetic conservation of interactions within a 
  set of 59 pollination and 11 herbivory networks. 
  These networks span a range of biomes 
  (desert to scrub forest to grassland) and countries (Sweden to 
  Australia), and range in size between 18 and 996 total species 
  (mean 160.93, median 96) with seven to 131 plant species (mean 38.06, 
  median 28).
  To ensure that we were analysing interactions influenced by similar
  sets of traits across networks, we restricted our herbivory 
  networks to insects consuming leaves. This excluded sap-sucking, 
  leaf-mining, and galling insects as well as seed predators and
  xylophagous insects; all of these interactions involve different 
  plant tissues and means of feeding
  than leaf consumption and so may be influenced by different
  plant and insect traits. The bulk of our herbivory networks 
  included only leaf-chewing insects. Where a network contained other
  types of herbivores we removed the non-leaf-chewing insects. Any
  plants which had no interaction partners after removing other types
  of herbivores were also removed. We also excluded networks which focused on
  plants from a single genus as these did not contain sufficient
  variation in phylogenetic distance between plants. This left us
  with a final data set of 54 pollination and 11 herbivory networks.
  See \emph{Table S1, Supporting Information} for details on the original 
  sources of all networks.

>>>>

  [[update refs, add definition of plant roles]]
  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals~\citep{Schemske1999}.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015}.
  In particular, significant phylogenetic signal in plants' interaction partners
  ---the tendency for more closely-related plants to have more similar interactions---
  tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015}; but see~\citealp{Elias2013,Fontaine2015}).
  Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
  animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]]

@@

  A further complication is the possibility that the relationship between
  plants' relatedness and the similarity of their interaction partners is
  not constant across plant clades. Closely-related plants
  in one clade might be under strong selection to favour dissimilar
  sets of pollinators to avoid exchanging pollen with other
  species~\citep{Levin1970,Bell2005,Mitchell2009}. Similar pressures 
  could also affect related plants' defences against herbivores if 
  congeners tend to grow in the same places such that herbivores 
  could easily move between them.  Unrelated plants might also 
  converge upon similar phenotypes, attracting a particularly 
  efficient or abundant pollinator~\citep{Ollerton1996,Ollerton2009}. 
  Likewise, herbivores may be able to depredate sets of unrelated 
  plants if the plants have evolved similar defences~\citep{Pichersky2000}. 
  In either case, dissimilarity of interactions among related species 
  or similarity of interactions among unrelated species could result 
  in weaker phylogenetic signal across an entire plant community. 
  Moreover, all of the aforementioned hypotheses 
  are non-exclusive; different processes likely affect different
  clades, and these processes might be associated with different 
  pressures imposed by pollination and herbivory.

  Here we use a novel approach to investigate how overlap in 
  interaction partners between pairs of plants (henceforth ``niche 
  overlap'') varies over phylogenetic distance. Whereas previous 
  studies have focused on the presence or absence of phylogenetic
  signal across entire networks, we are able to investigate the
  relationship between niche overlap and phylogenetic distance in
  within networks as well as different plant families. Specifically,
  we test whether niche overlap decreases over increasing phylogenetic
  distance in a large dataset of pollination and herbivory networks, 
  whether the plant family composition of a community affects the
  relationship between niche overlap and phylogenetic distance in that 
  community, and whether the relationship between niche overlap and 
  phylogenetic distance differs across plant families.

@@

  We studied tested for phylogenetic signal in niche overlap within a 
  set of 59 pollination and 11 herbivory networks. These networks span 
  a range of biomes (desert to scrub forest to grassland) and 
  countries (Sweden to Australia). The herbivory networks included a 
  variety of types of herbivores but were dominated by insects 
  consuming leaves. To ensure that we were analysing interactions 
  influenced by similar sets of traits across networks, we restricted 
  our herbivory networks to insects consuming leaves and excluded 
  sap-sucking, leaf-mining, and galling insects as well as seed 
  predators and xylophagous insects; all of these interactions involve 
  different plant tissues and means of feeding than leaf consumption 
  and so may be influenced by different plant and insect traits. 
  Specifically, we removed any non-leaf consuming insects and any 
  plants which had no interaction partners after removing other types  
  of herbivores. The adjusted networks range in size between 19 and 
  997 total species (mean=162, median=97) with  between 8 and 132 
  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
  Supporting Information} [[NOT DONE!]]for details on the original sources of all 
  networks.
